Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-24 ms.tex
captions

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
 2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
%   0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
%   0.1 & \eddrt \gsim 0.1
% \end{cases}
\label{eq:efficiency}
\end{align}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to
  the gas heating rate in galactic nuclei at time $\tau_{\star}$ after
  a single burst of star formation.  Top and bottom panels show cases
  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
  (both cusps).  Solid and dashed lines show the ranges of
  $\tau_{\star}$ for which the accretion flow is thermally stable and
  unstable, respectively, according to the ratio of $\dot{q}_{\rm
    heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius
  (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
  are the values of the stellar velocity dispersion, $\sigma_0$,
  approximated as $\sqrt{3} \sigma_{\bullet}$, where
  $\sigma_{\bullet}$ is the velocity dispersion from the $\Mbh-\sigma$
  relation \citep{McConnellMa+:2011a}.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}):
  stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a};
  see Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:}
  The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
  v_{w}^{2}$) from the top panel to the radiative cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter $\eta$
  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star SFHs
  from \citealt{MosterNaab+:2013a} (blue) and the ratio of Ia radius to
  stagnation radius as a function of $\Mbh$ (green).}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} ( (\alpha/0.1) 0.1 \eddr) $, where
  $\epsilon_{\rm rad}$ is given by equation~\eqref{eq:efficiency} and
  $\eddr$ corresponds to the gas inflow rate on large scales.  Shown
  for comparison are the X-ray luminosities calculated for the maximum
  thermally-stable accretion rate ({\it dashed orange line};
  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
  heating-regulated accretion rate ({\it dashed pink line};
  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
  corresponding to each SMBH mass.}
\end{figure*}

@@

Perhaps a more readily addressable test is whether a steady-state
accretion picture developed in this work can account for the the large
scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at least
three effects: (1) intrinsic scatter in the scaling relationships
($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to measure $\Mbh$; (2)
the strong sensitivity of the accretion rate to the stellar wind
velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix
\ref{fig:NickPlot2}), this can lead to order of magnitude differences
in $\dot{M}$; (3) differences in angular momentum of the infalling gas
from galaxy to galaxy, resulting in differences in the fraction of the
gas lost to outflows.  Also potentially contributing is the order of
magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between
$\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).
Differences in $\dot{M}$ are augmented by the theoretical expectation
that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
flows.

>>>>

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
 2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
%   0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
%   0.1 & \eddrt \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to
  the gas heating rate in galactic nuclei at time $\tau_{\star}$ after
  a single burst of star formation.  Top and bottom panels show cases
  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
  (both cusps with $\Gamma=0.8$).  Solid and dashed lines show the ranges of
  $\tau_{\star}$ for which the accretion flow is thermally stable and
  unstable, respectively, according to the ratio of $\dot{q}_{\rm
    heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius
  (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
  are the values of the stellar velocity dispersion, $\sigma_0$,
  approximated as $\sqrt{3} \sigma_{\bullet}$, where
  $\sigma_{\bullet}$ is the velocity dispersion from the $\Mbh-\sigma$
  relation \citep{McConnellMa+:2011a}.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}): stellar
  wind heating ({\it orange}), Ia supernovae ({\it green}),
  millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
  Each heating source varies with black hole mass $\Mbh$ calculated
  for average SFHs from \citet{MosterNaab+:2013a}; see
  Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
  v_{w}^{2}$) from the top panel to the radiative cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter
  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star SFHs
  from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
  stagnation radius as a function of $\Mbh$ (green), and the ratio of
  the normalized heating rate
  $\zeta=\sqrt{1+\frac{v_w^2}{\sigma_0^2}}$ to the critical heating
  rate $\zeta_c$ for which no outflow is possible (see
  eq.~\eqref{eq:zetacrit}). In evaluating the latter quantity we use
  scaling relations for $r_b$, $\rinf$, and $\Gamma$ based on
  \citet{LauerFaber+:2007a}. {\bf AG added the zeta/zetac line}.}

 % $\Gamma=0.3
 %  \Mbheight^{-0.24}$, $\rinf=14 \Mbheight^{0.6}$ pc
 %  (eq~\eqref{\eqref{eq:rsoi}}), $\rb\simeq 106 \Mbheight^{0.39} $ pc
 %  (for $\Gamma<0.3$), and $\rb\simeq 100$ pc (for $\Gamma\geq 0.3$)
 %  {\bf Added zeta/zeta_c line but unfortunately caption became
 %    somewhat verbose (I don't think all of this description is
 %    necessary--maybe just say we use scaling relations based on Lauer
 %    et al. sample?) Also being so close to zeta/zeta_c=1 implies
 %    there is a limit to how much scatter we could explain just by
 %    variations in the heating rate}.

\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} ( (\alpha/0.1) 0.1 \eddr) $, where
  $\epsilon_{\rm rad}$ is given by equation~\eqref{eq:efficiency} and
  $\eddr$ corresponds to the gas inflow rate on large scales.  Shown
  for comparison are the X-ray luminosities calculated for the maximum
  thermally-stable accretion rate ({\it dashed orange line};
  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
  heating-regulated accretion rate ({\it dashed pink line};
  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
  corresponding to each SMBH mass.}
\end{figure*}

@@

Perhaps a more readily addressable test is whether a steady-state
accretion picture developed in this work can account for the the large
scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at least
three effects: (1) intrinsic scatter in the scaling relationships
($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to measure $\Mbh$; (2)
the strong sensitivity of the accretion rate to the stellar wind
velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix
\ref{fig:NickPlot2}), this can lead to order of magnitude differences
in $\dot{M}$ {\bf AG limitation from zetac}; (3) differences in
angular momentum of the infalling gas from galaxy to galaxy, resulting
in differences in the fraction of the gas lost to outflows.  Also
potentially contributing is the order of magnitude difference, at
fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp
galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are
augmented by the theoretical expectation that $L_{\rm X} \propto
\dot{M}^{2} $ for radiatively inefficient flows.
